---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plantr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/mikemahoney218/plantr/workflows/R-CMD-check/badge.svg)](https://github.com/mikemahoney218/plantr/actions)
<!-- badges: end -->

The goal of plantr is to provide a simple R wrapper around the 
[USDA PLANTS Database](https://plants.sc.egov.usda.gov/java/citePlants) API,
allowing users to easily download data on plant species as a part of their 
regular workflow. 

## Installation

You can install the development version of plantr with:

``` r
remotes::install_github("mikemahoney218/plantr")
```

## Usage

`plantr` is a little seedling of a package at the moment, without much in the 
way of higher-order functions. With that said, the main workhorse of the package
is already implemented as `ptr_search`, letting you search the PLANTS Database
directly from R. Searching the basic API (which returns data on plant names and
USDA symbols) is as simple as:

```{r}
library(plantr)

ptr_search(common_name = "balsam fir")
```

The full API may also be searched by setting `basic` to `FALSE`. Note that this 
example uses a single USDA plant symbol in order to speed up processing time:

```{r}
ptr_search(symbol = "ABBAB", basic = FALSE)
```

Please note that `plantr` is still in an experimental phase, and breaking 
changes may happen to any function as development continues.
